Overlooked Dynamics in Algorithmic Recourse

### 2022-07-05 paper/sections/introduction.qmd
set up template for paper

@@

![Dynamics in Algorithmic Recourse: we have a simple Bayesian model trained for binary classification (a); the implementation of AR for a random subset of individuals leads to a domain shift (b); as the classifier is retrained we observe a model shift (c); as this process is repeated, the decision boundary moves away from the target class (d).](poc.png){#fig-dynamics fig.pos="h" width=45%}

>>>>

# Introduction {#intro}

@@

![Dynamics in Algorithmic Recourse: we have a simple Bayesian model trained for binary classification (a); the implementation of AR for a random subset of individuals leads to a domain shift (b); as the classifier is retrained we observe a model shift (c); as this process is repeated, the decision boundary moves away from the target class (d).](www/poc.png){#fig-dynamics fig.pos="h" width=45%}
